---
title: "index.qmd"
format: html
author: 
  - Young Ju Nam
  - Serenity Fan 
editor: visual
execute:
      warning: false
---

# DATA EXPLORATION

The data source employed in the creation of the following visualisizations are the [Seoul City government water quality statistics](https://data.seoul.go.kr/dataList/342/S/2/datasetView.do) . We note that, where appropriate, Korean titles/words have been translated into English by Nam. The data includes several water indicators, for neighborhoods within Seoul, over the time period from 1996-2022. 

```{r}
#| echo: false

rm(list=ls()) 

# install relevant packages
library(readxl)
library(dplyr)
library(tidyr)
library(tidyverse)
library(janitor)
library(readxl)
library(sampling)
library(haven) 
library(srvyr)
library(ipumsr)
library(janitor)
library(ggplot2)


```

# DATA CLEANING

We begin by loading the data, transforming it from its initial form (with nearly 200 variables!) into 'tidy data' form, such that each observation is a year-neighborhood observation of 7 water quality measurements. We also assign/classify each of these observations into three grades of water quality: "Good", "Normal", and "Bad", based upon the WRMIS (Water Resource Management Information System of South Korea) Water Quality Criteria. 

```{r, results='hide', message=FALSE, warning=FALSE}
# #Remove X's from variable names 
# for ( col in 1:ncol(data) ){
#     colnames(data)[col] <- sub("X", "", colnames(data)[col])
# }
# 
# for ( col in 1:ncol(data) ){
#     colnames(data)[col] <- sub("\\.", "_", colnames(data)[col])
# }
# 
# data <- data %>%
#   rename_all(~ ifelse(grepl("_", .), ., paste0(., "_0")))
# 
# # #Remove .* 
# # names(data) <- sub("\\.{1}\\d*$", "", names(data))
# 
# data <- rename(data, Region = Year_0)
# 
# #Pivot 
# data_tidy <- data %>% 
#   pivot_longer(
#     cols = !Region,
#     names_to = c("year", "measure_type"),
#     names_sep = "_",
#     values_to = "Value"
#   )
# 
# data_tidier <- data_tidy %>% 
#   janitor::clean_names() %>% 
#   mutate_all(~as.character(.)) %>% 
#   pivot_longer(-parameter) %>%
#   mutate(name = str_remove_all(name, "...[0-9].*")) %>% 
#   mutate(year = rep(rep(1996:2022, each = 7), 25)) %>% 
#   pivot_wider(id_cols = c(year, parameter), names_from = name, values_from=value)


# load download data
korea_waterdata <- read_csv("data/korea_waterdata.csv", skip = 1)

# tidy data
org_data <- korea_waterdata %>% 
  janitor::clean_names() %>% 
  mutate_all(~as.character(.)) %>% 
  pivot_longer(-parameter) %>%
  mutate(name = str_remove_all(name, "_[0-9].*")) %>% 
  mutate(year = rep(rep(1996:2022, each = 7), 25))%>% 
  pivot_wider(id_cols = c(year, parameter), names_from = name,     
  values_from = value)

org_data <- org_data %>% 
  arrange(year, parameter)


# Assign 3 categories of water quality based on government criteria contained within document "data/Copy of Water_quality_criteria(WRMIS)(1)"
quality_added_data <- org_data %>%
   mutate_at(c('year', 'water_temperature_c', 'potential_of_hydrogen_p_h',
               'dissolved_oxygen_do_mg_l', 'biochemical_oxygen_demand_bod_mg_l',
               'chemical_oxygen_demand_cod_mg_l', 'suspended_solid_ss_mg_l',
               'coliform_bacteria_mpn'), as.numeric) %>% 
   mutate(quality = case_when(
                       6.5 <= potential_of_hydrogen_p_h &
                       8.5 >= potential_of_hydrogen_p_h &
                       dissolved_oxygen_do_mg_l >= 5.0 &
                       biochemical_oxygen_demand_bod_mg_l <= 3.0 &
                       chemical_oxygen_demand_cod_mg_l <= 5.0 &
                       suspended_solid_ss_mg_l <= 25.0 &
                       coliform_bacteria_mpn <= 1000.0 ~ "Good",
                       
                       6.5 <= potential_of_hydrogen_p_h &
                       8.5 >= potential_of_hydrogen_p_h &
                       dissolved_oxygen_do_mg_l >= 5.0 &
                       biochemical_oxygen_demand_bod_mg_l <= 5.0 &
                       chemical_oxygen_demand_cod_mg_l <= 7.0 &
                       suspended_solid_ss_mg_l <= 25.0 &
                       coliform_bacteria_mpn <= 5000.0 ~ "Normal",
          
                       dissolved_oxygen_do_mg_l >= 2.0 &
                       biochemical_oxygen_demand_bod_mg_l <= 99.0 &
                       chemical_oxygen_demand_cod_mg_l <= 99.0 &
                       suspended_solid_ss_mg_l <= 999.0 &
                       coliform_bacteria_mpn <= 999999999.0 ~ "Bad")
)

# DATA CLEANING



# # tidy data
# tidy_data <- data %>% 
#   janitor::clean_names() %>% 
#   mutate_all(~as.character(.)) %>% 
#   pivot_longer(-parameter) %>%
#   mutate(name = str_remove_all(name, "_[0-9].*")) %>% 
#   mutate(year = rep(rep(1996:2022, each = 7), 25))%>% 
#   pivot_wider(id_cols = c(year, parameter), names_from = name, values_from = value)


```

```{r}
#Clean-up variable names 
quality_added_data <- quality_added_data %>% 
  rename(region = parameter, water_temp = water_temperature_c, pH = potential_of_hydrogen_p_h, dissO2 = dissolved_oxygen_do_mg_l, biochemO2 = biochemical_oxygen_demand_bod_mg_l, chemO2 = chemical_oxygen_demand_cod_mg_l, ss = suspended_solid_ss_mg_l, coli = coliform_bacteria_mpn)


```

# DATA VISUALIZATIONS

## Graph 1: Water Temperature over Time 

Our first visualization shows water temperature data that have been averaged over all (available) Seoul neighborhoods. This (represented by the blue line) indicates a high degree of variance over time, ranging from a low of ~14.2C in 1996 to a high of ~16.3C in 2001. However, the red dashed line, which is a smoothed trend line generated using the "geom_smooth()" geometry, reveals that underneath this temporal variation lies a small increase average water temperature, from ~15.2C in 1996 to 15.5C in 2022. Given the dispersion/overlap in this smoothing estimate however (grey area), it is not clear whether this increase is statistically significant. In future, a comparison with air temperature trends (in the same neighborhoods) could be a good way of validating the measurements. 

```{r, results='hide', message=FALSE, warning=FALSE}
# Graph 1: Average temperature

library(ggplot2)

temp_data <- quality_added_data %>%
  group_by(year) %>%
  summarize(avg_temp = mean(water_temp, na.rm =TRUE))

ggplot(data = temp_data) +
  geom_line(mapping = aes(x = year, y = avg_temp), color = "blue") +
  geom_smooth(mapping = aes(x = year, y = avg_temp), color = "red", linetype = "dashed") + 
  labs(
    title = "Average (Blue) and Smoothed (Red) Water Temperature over Seoul neighborhoods, 1996-2022",
    subtitle = "Source: Water Resource Management Information System of South Korea (http://www.wamis.go.kr/wke/wke_wqbase_lst.do)",
    x = "Year",
    y = "Temperature (C)"
  ) + 
    theme(plot.title = element_text(size = 10)) + 
    theme(plot.subtitle = element_text(size = 7))

# 
# # Graph 2: Quality Proportions
# 
# temp2_data <- quality_added_data %>% 
# group_by(year) %>%
# filter(!is.na(quality)) %>%
# count(quality) %>%
# mutate(p = n / sum(n))
# 
# ggplot(data = temp2_data) +
#   aes(x = year, y = p, fill = quality) +
#   geom_col() +
#   labs(
#     title = "Proportions of Categorical Variable by Year",
#     subtitle = "1996-2022", 
#     x = "Year",
#     y = "Proportion"
#   )
#            
# 
# # Graph 3: Correlation between biochemical_oxygen_demand & chemical oxygen demand
# 
# ggplot(data = quality_added_data) +
#   geom_point(mapping = aes(x = biochemO2, y = chemO2)) + 
#   labs(
#     title = "Biochemical Oxygen Demand and Chemical Oxygen Demand",
#     subtitle = "1996-2002 Data",
#     x = "Biochemical Oxygen Demand [mg/L]",
#     y = "Chemical Oxygen Demand [mg/L]"
#   )
# 
# # Graph 4: Correlation between potential of hydrogen & dissolved oxygen
# 
# ggplot(data = quality_added_data) +
#   geom_point(mapping = aes(x = pH, y = dissO2)) + 
#   labs(
#     title = "Correlation between pH and Dissolved O2",
#     subtitle = "1996-2002 Data", 
#     x = "pH",
#     y = "Dissolved Oxygen Content [mg/L]"
#   )

```

## Graph 2: Trends in Water Quality over Time 

We construct a record of the changes in the proportions of 3 kinds of water quality (Bad, Normal, Good) over time. It should be noted that we removed all "NA" designations, which could arise through either: a) the fact that the number of neighborhoods measured increased significantly over the time period of this dataset, such that new neighbhorhoods have 'NA' data in earlier years prior to their creation, or b) the fact that the Quality criteria are not mutually exclusive. Ideally, we could have created an index, weighing and aggregating the 7 different quality measures. However, we were not able to do this, owing to time constraints, and the subjectivity of creating such an index. These factors notwithstanding, our quality measure indicates that Seoul water is overwhelmingly of 'Bad' quality - with some small improvement over time, reflected in larger numbers of 'Normal' and 'Good' neighborhoods over the period 2000-2022. 

```{r, results='hide', message=FALSE, warning=FALSE}
# Graph 2: Quality Proportions

temp2_data <- quality_added_data %>% 
  group_by(year) %>% 
  filter(!is.na(quality)) %>% 
  count(quality) %>% 
  mutate(p = n/sum(n)) 

ggplot(data = temp2_data) + 
  aes(x = year, y = p, fill = quality) + 
  geom_col() + 
  labs(
    title = "Proportions of Water Quality by Year, over Seoul Neighborhoods, 1996-2022",
    subtitle = "Source: Water Resource Management Information
    System of South Korea
    (http://www.wamis.go.kr/wke/wke_wqbase_lst.do)",
    x = "Year",
    y = "Proportion of Measurements in Category",
    fill = "Quality"
  ) +
    theme(plot.title = element_text(size = 12))
    theme(plot.subtitle = element_text(size = 10))

# ggplot(data = quality_added_data) +
#   geom_bar(aes(y = (..count..)/sum(..count..), x = year, fill = quality)) + 
#   labs(
#     title = "Proportions of Categorical Variable by Year, 1996-2022",
#     subtitle = "Source: Water Resource Management Information System of South Korea (http://www.wamis.go.kr/wke/wke_wqbase_lst.do)", 
#     x = "Year",
#     y = "Proportion",
#     fill = "Quality"
#   ) + 
#     theme(plot.subtitle = element_text(size = 6))
```


## Graph 3: Correlation between Biochemical and Chemical Oxygen Demand 

We observe a positive relationship between biochemical oxygen demand (BOD), and chemical oxygen demand, measured in mg/L. The former, 

```{r, results='hide', message=FALSE, warning=FALSE}
# Graph 3: Correlation between biochemical_oxygen_demand & chemical oxygen demand

ggplot(data = quality_added_data) +
  geom_point(mapping = aes(x = biochemO2, y = chemO2), color = "black", alpha = 0.3) + 
  labs(
    title = "Biochemical Oxygen Demand and Chemical Oxygen Demand, 1996-2022",
    subtitle = "Source: Water Resource Management Information System of South Korea (http://www.wamis.go.kr/wke/wke_wqbase_lst.do)", 
    x = "Biochemical Oxygen Demand [mg/L]",
    y = "Chemical Oxygen Demand [mg/L]"
  ) + 
  theme_minimal() + 
  theme(plot.subtitle = element_text(size = 7))
```



## Graph 4: Disaggregation by Neighborhood of Suspended Solid and Coliform Bacteria Content from 1996-2022 

```{r, results='hide', message=FALSE, warning=FALSE}
#Graph 4: 

ggplot(data = quality_added_data) + 
    geom_point(mapping = aes(x = ss, y = log(coli), color = region), size=1.5, alpha = 0.5) +
     labs(
      title = "Suspended Solids and Coliform Bacteria Concentration by Neighborhood, 1996-2022",
      subtitle = "Source: Water Resource Management Information System of South Korea (http://www.wamis.go.kr/wke/wke_wqbase_lst.do)", 
      x = "Suspended Solid Content [mg/L]",
      y = "log(Coliform [MPN/100mL])"
          ) +
  theme(plot.title = element_text(size = 11)) + 
  theme(plot.subtitle = element_text(size = 7))


```
